Code for Breast Cancer Pain Study

### 2021-02-18 manuscript_code_20201004.Rmd
total days

final.table0 = merge(final.adj.1,final.adj.2,by="vars",all=T)
final.table1 = merge(final.table0,final.unadj,by="vars",all=T)
# which(! table.explvars %in% final.table0$vars)
# which(! final.table0$vars %in% table.explvars)
final.table = final.table1[match(table.explvars,final.table1$vars),c(10:13,2:9)]
rownames(final.table) = table.explvars

>>>>

final.table0 = merge(final.adj.1,final.adj.2,by="vars",all=T)
final.table1 = merge(final.table0,final.unadj,by="vars",all=T)
# which(! table.explvars %in% final.table0$vars)
# which(! final.table0$vars %in% table.explvars)
final.table = final.table1[match(table.explvars,final.table1$vars),c(10:13,2:9)]
rownames(final.table) = table.explvars
final.table[grepl(pattern="zero",rownames(final.table)),c(1:3,5:7,9:11)] = apply(final.table[grepl(pattern="zero",rownames(final.table)),c(1:3,5:7,9:11)],2,
                  function(x) {
                    return(round(1/x,digits=3))
                  })
final.table[grepl(pattern="zero",rownames(final.table)),c(2,3)] = final.table[grepl(pattern="zero",rownames(final.table)),c(3,2)]

final.table[grepl(pattern="zero",rownames(final.table)),c(6,7)] = final.table[grepl(pattern="zero",rownames(final.table)),c(7,6)]

final.table[grepl(pattern="zero",rownames(final.table)),c(10,11)] = final.table[grepl(pattern="zero",rownames(final.table)),c(11,10)]
